Quality measure notes

### 2021-06-13 StateOfPractice/Ao-Report/13Methods.tex
Ao's report - updated ch 3

Our method involves: 1) choosing a software domain (Section \ref{sec_domain_selection}); 2) collecting and filtering software packages (Section \ref{sec_software_selection}); 3) grading the selected software (Section \ref{sec_grading_software}); 4) interviewing development teams for further information (Section \ref{sec_grading_software}).

@@

The only ``mandatory'' requirement is that the software must be OSS, as defined in Section \ref{sec_open_source_software}. This is due to the grading process defined int Section \ref{sec_grading_template}. To evaluate all aspects of some software qualities, the source code should be accessible.

>>>>

Our method involves: 1) choosing a software domain (Section \ref{sec_domain_selection}); 2) collecting and filtering software packages (Section \ref{sec_software_selection}); 3) grading the selected software (Section \ref{sec_grading_software}); 4) interviewing development teams for further information (Section \ref{sec_interview_methods}).

@@

The only ``mandatory'' requirement is that the software must be OSS, as defined in Section \ref{sec_open_source_software}. The reason is that to evaluate all aspects of some software qualities, the source code should be accessible.
